\textit{Supplementary materials for}: Text embedding models reveal high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-01-27 paper/supplement.tex

\author{Paxton C. Fitzpatrick\textsuperscript{1} and Jeremy R.
Manning\textsuperscript{*, 1}\\\textsuperscript{1}Dartmouth
College\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

>>>>

\author{Paxton C. Fitzpatrick\textsuperscript{1},
Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
Manning\textsuperscript{1, *}\\\textsuperscript{1}Dartmouth
College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}
